\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-08-30 paper/manuscript.tex
added removal of terms that are more common in city than in corpus (by a threshold); removal of city names; short addition to paper explaining reason for using Arun et al. 2010 measure

>>>>

%Justicifcation for Arun 2010 topic number measure
In order to determine the optimal number of topics for our corpus, we utilize the measure developed by \cite{Arun2010}. In contrast to other approaches such as \cite{Cao2009} or \cite{Griffith2004}, this measure includes as much information about the model as possible by taking into account both the document-term matrix, as well as the word-topic matrix. We find 200 topics to be the best value (see figure \ref{ldatuning}).
